A Domain Specific Language for SpectreGuard

### 2020-12-11 paper/main.tex
paper: 'obfuscate' operations and conditional entropy

>>>>

Another possible avenue of future work is the creation of ``obfuscate''
operations: operations which change the contents of secret variable in such a
way that it is not feasible to recover the original contents. An example is a
hash function. This could be a mechanism to go from a secret variable to a
public variable. The type system and analysis tool could then be modified to
account for this. Perhaps it is also possible to allow the programmer to create
new obfuscate functions, maybe using a restricted subset of the language. Also,
it might be possible to use information theory concepts, like the conditional
entropy~\cite{InfoTheory} of the function output conditioned on its input, to create a framework
to statically provide assurance that there is a certain limit on how much
information could be theoretically recovered (in general) after such a
programmer-defined obfuscate function is applied.
